\Chris{This is a very rough draft. I want to get it right, but imagine my first draft doesn't need the final version.}

I am a firm believer that people often arrive at their destination not on their own, but instead with a great amount of help from a great many people. That is surely true in my case. 
I would like to thank the folks who helped me arrive at this point in my educational journey. Thank you to my family. Claire, Terry and Gary, you know me unlike anyone else in the world. Thank you to my teachers from Nairobi, Kuala Lumpur and Stanford. 
%The long list includes: Paul Anderson, Gary Blanton, Rick Bisset, Noren Sahari, Eric Roberts and Mehran Sahami. Thank you to my advisors Leonidas Guibas and Mehran Sahami. 
\Chris{Part redacted for now because it involves readers...}

Five of the chapters in this book are derived from papers published in conferences and reflect collaborative work. I would like to express my deep gratitude to all the co-authors. Whether or not you directly contributed to a result that became part of my thesis, you helped form my thoughts. In addition to my advisors I would like to thank: Jon Huang, Jascha Sohl-Dickstein, Emily Schneider, Andy Nguyen, Jon Bassen, Surya Ganguli, Rene Kizilcec, Daphne Koller, Andrew Ng, Steve Cooper, Chuong Do, Zhenghao Chen and John Mitchell. You were a pleasure to work with! I would like to take a moment to especially thank Jon Huang. As a post doc you were a wonderful role model both with respect to research and as an outstanding person.

Thank you to all the people who did the hard work of building courses and collecting material. And then, graciously allowed me to analyze your data. Special thanks to Khan Academy, Code.org, Stanford CS106A, Coursera Machine Learning and Coursera Human Computer Interaction and Assistments. Special thanks to Nan Li, Ellen Spertus, Chinmay Kulkarni, Scott Klemmer and Andrew Ng who were the individuals behind those interactions. 

Chris Piech is supported by NSF-GRFP grant number DGE-114747 and the VPOL grant. 
